%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{graphicx}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage[urw-garamond]{mathdesign}
% \usepackage{charter}
%\usepackage{lmodern}
\usepackage[OT1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{1.10in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.00\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{{\small #1}} & {{\textbf{\small #2}}} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \emph{}{\small#1} & \emph{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \upshape Victor Kreitmann} \\ \vspace{1pt}
    %123 Street Name, Town, State 12345 \\ \vspace{1pt}%
    \small \raisebox{-0.1\height}\faPhone\ +33.7.68.62.97.17~
    \href{https://www.linkedin.com/in/victor-kreitmann/}{\raisebox{-0.2\height}\faLinkedin\ \underline{Linkedin}}  ~    
    \href{mailto:victor.kreitmann@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{victor.kreitmann@gmail.com}} ~ 
    \vspace{0pt}
\end{center}




%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sciences Po}{2022 - 2024}
      {Master's degree, Development Economics}{Paris, France}
      
      \resumeSubheading
      {École normale supérieure (ENS Ulm)}{2021 - 2024}
      {Master's degree, Geography \& Geopolitics}{Paris, France}
      \resumeItemListStart
      \resumeItem{\underline{M1 Thesis}: Natural disasters, war- or peace-makers? Measuring natural disasters' effects on violent intrastate conflicts.\emph{(in French, \href{https://drive.google.com/file/d/1O6ke_2wZjExpSnBBnSKN7shPb0E3ZBgg/view?usp=sharing}{\underline{here}})}}
      \resumeItemListEnd
      
      \resumeSubheading
      {Université Paris II Panthéon-Assas}{2020 - 2021}
      {Bachelor's degree, Law}{Paris, France}
      \resumeItemListStart
      \resumeItem{GPA: 14.5/20}
      \resumeItemListEnd
      
      \resumeSubheading
      {McGill University}{2017 - 2020}
      {Bachelor's degree, Political Science}{Montreal, QC}
      \resumeItemListStart
      \resumeItem{First Class Honours. GPA: 3.64/4.00}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------EXPERIENCE-----------
\section{Experiences}
  \resumeSubHeadingListStart

    \resumeSubheading
      {General Secrétariat for European Affairs - Borders, Migrations \& Asylum}{April - September 2022}
      {Project Intern}{Paris, France}
      \resumeItemListStart
        \resumeItem{Monitored the EU response to the Ukrainian refugee crisis and contributed to communicating France's response to the European Commission and EU member states.}
        \resumeItem{Contributed to structuring France's position and diplomatic actions in Justice \& Home Affairs' matters: negotiations of the Eurodac regulation, the Solidarity Declaration, and the reform of the Schengen Borders Code.}
      \resumeItemListEnd

    \resumeSubheading
      {Paris School of Economics/Harvard University}{May - October 2021}
      {Research Assistant (part-time)}{Paris, France}
      \resumeItemListStart
        \resumeItem{Research on expressive voting \& candidates' electoral positioning and communication in cantonal and legislative elections, using election manifestos.}
        \resumeItem{Mainly performed data collection and data cleaning/dataset organization.}
    \resumeItemListEnd
    
    \resumeSubheading
      {French Ministry of Defence - Higher Militar Education Department}{January - June 2021}
      {Project Intern}{Paris, France}
      \resumeItemListStart
        \resumeItem{Conducted research to support the development of new training material for senior officers' training at the \emph{École de Guerre}: geopolitics of cyberspace, space militarization, climate change \& the military, international humanitarian law, etc.}
    \resumeItemListEnd
    
     \resumeSubheading
      {French National Court of Asylum - Research Office}{July - December 2020}
      {Research Intern}{Paris, France}
      \resumeItemListStart
        \resumeItem{Conducted research on the political and security situation as well as the main threats to human rightsg in asylum-seekers' countries of origins: country-report focused on Mauritania, report on the Sahel's main jihadi groups, report on the 2020 Sudanese Peace Agreement, etc.}
        \resumeItem{Developed and implemented a methodology used to estimate violence levels by region using ACLED data.}
    \resumeItemListEnd      

     \resumeSubheading
      {National Taiwan University}{April - June 2020}
      {Research Assistant (part-time)}{Taipei, Taiwan}
      \resumeItemListStart
        \resumeItem{Conducted research on the interactions between Covid-19 and Chinese domestic politics.}
        \resumeItem{Mainly performed literature review in French and English, of both academic and grey literature.}
      \resumeItemListEnd  
  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
\vspace{-4pt}
 \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
    \textbf{General}{: Research, writing, critical thinking, adaptability, problem-solving, attention to detail, work ethic.} \\
     \textbf{Technical (still learning!)}{: R, \LaTeX,  R Markdown, GitHub, Google Sites.} \\
     \textbf{Languages}{: French (native), English (bilingual), Spanish (B2), Chinese (B1/A2).} \\
    }}
 \end{itemize}
 \vspace{-10pt}
 
\section{Interests}
\vspace{-4pt}
 \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
    \textbf{Academic/Professional}{: Development, migration, public policy evaluation, intrastate conflits/insecurity.} \\
    \textbf{Personal}{: Chess, podcasts, non-fiction books, bouldering, scientific vulgarization.} \\
%     \textbf{Technical (still learning!)}{: R, \LaTeX, GitHub,  Google Sites} \\
    }}
 \end{itemize}
 
\begin{center}
    \emph{Academic \& professional recommendations available upon request}.
\end{center}
 
\end{document}
